Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
modif expe full resolution

\subsection{Per Vertex Real-time Computation on GPU}

@@

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top and middle show results of curvature tensor estimation
(mean, Gaussian curvature, first and second principal curvatures, first and
second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
shows the mean curvature estimation in real-time on a dynamic object. For all
illustrations, we use directly normal vectors computed by algorithm discussed in
Section~\ref{sec:curv-tens-estim}.

We compare the approximation made to accelerate visualisation with the ground
truth result obtained at level $l_0$. We also compare it with the hierarchical
algorithm. The results are presented Table~\ref{tab:full-res-stat}, and
illustrated Figure~\ref{fig:refine}.

>>>>

\subsection{Per Vertex Real-time Computation on GPU}
\label{sec:hierarchical}

@@

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top and middle shows results of curvature tensor
estimation (mean, Gaussian, first and second principal curvatures, first and
second principal directions) on an OctaFlower at level $l_0$ (ground truth).
Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
dynamic object. For all illustrations, we use directly normal vectors computed
by algorithm discussed in Section~\ref{sec:curv-tens-estim}.

Then, we compare the approximation made by computing curvature from level $l >
l_0$ in order to accelerate visualisation with the ground truth result obtained
at level $l_0$. We also compare them with the hierarchical algorithm discussed
in Section~\ref{sec:hierarchical}. The results are presented in
Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.
